Optimal Particle Paths Around Points in $\R^2$ with Constrained Acceleration

### 2013-10-08 path_theorems.tex
Adding more filler words.

@@

\begin{theorem}
  Let particle $p$ have initial velocity $\bvec{v}$ and starting position $\bvec{X}_0$. Let $p$ have constant speed conditions and let the end position be $\bvec{X}_f$ such that $d(\bvec{X}_f, \bvec{X}_0) > R_{min}$. The fastest path $\bhat{\gamma_p}$ for particle $p$ to reach $\bvec{X}_f$ minimizes $\theta(t)$ for all $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$.
  \label{theorem:restricted-theta}
\end{theorem}
\proof Let $p_1$ be a particle whose path $\gamma_{p_1}$ is determined by the minimizing $|\theta(t)|$ for all times $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$. We shall show that $\gamma_{p_1}$ is in fact the fastest path to $\bvec{X}_f$.

>>>>

We can also prove that this fastest path is unique without very much extra work.

@@

\begin{theorem}
  Let particle $p$ have initial velocity $\bvec{v}$ and starting position $\bvec{X}_0$. Let $p$ have constant speed conditions and let the end position be $\bvec{X}_f$ such that $d(\bvec{X}_f, \bvec{X}_0) > R_{min}$. The fastest path $\bhat{\gamma_p}$ for particle $p$ to reach $\bvec{X}_f$ minimizes $\theta(t)$ for all $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$.
  \label{theorem:restricted-theta}
\end{theorem}
\proof Let $p_1$ be a particle whose path $\gamma_{p_1}$ is determined by the minimizing $|\theta(t)|$ for all times $t \in [T_0(\gamma_{p_1}), T_f(\gamma_{p_1})]$. We shall show that $\gamma_{p_1}$ is in fact the fastest path to $\bvec{X}_f$.
